---
title: "Coursera_DS_Inference_Project2"
author: "Atul"
date: "January 31, 2016"
output: html_document
---

LOAD THE ToothGrowth DataBase
-----------------------------------
```{r}
library(datasets)
data("ToothGrowth")
```


BASIC INFORMATION ABOUT THIS DATABASE
---------------------------------------
```{r}
str(ToothGrowth)
colnames(ToothGrowth)
rownames(ToothGrowth)
dim(ToothGrowth)
summary(ToothGrowth)
unique(ToothGrowth$dose)
```


EXPLORATORY DATA ANALYSIS
--------------------------

```{r}
hist(ToothGrowth$len)
boxplot(ToothGrowth$len)
plot(ToothGrowth$dose, ToothGrowth$len)

library(ggplot2)
ggplot(data=ToothGrowth, aes(dose, len)) + geom_bar() + geom_point() + facet_wrap(~supp)
```

Above plots illustrate that length might be increasing with number of doses and supplements, which we validate in below testing

HYPOTHESIS TESTING
-------------------
We check following null hypotheses

1) There is no significant difference in length with supplements

```{r}
t.test(len ~ supp, paired = F, var.equal = F, data = ToothGrowth)
```

We can not reject NULL hypthesis with this confidence interval.

2) There is no significant difference in length with dose

```{r}
# COMPARISON WITH 0.5 and 1.0
ToothGrowth1 <- subset(ToothGrowth, ToothGrowth$dose %in% c(0.5,1.0))
ToothGrowth2 <- subset(ToothGrowth, ToothGrowth$dose %in% c(1.0,2.0))
ToothGrowth3 <- subset(ToothGrowth, ToothGrowth$dose %in% c(0.5,2.0))
t.test(len ~ dose, paired = F, var.equal = F, data = ToothGrowth1)
t.test(len ~ dose, paired = F, var.equal = F, data = ToothGrowth2)
t.test(len ~ dose, paired = F, var.equal = F, data = ToothGrowth3)
```

High confidence for alternate hypothesis indicate that we can reject NULL hypothesis.

We made some assumption while checking above hypothesis:-

* There might be other variables affecting data, which is missing in given ToothGrowth dataset.
* There might be mistake in collecting data.
* There might be affect of one dose into others does, if same guinea pig is tries with all doses.
* It might not blind-eyed test i.e. guinea pig might be aware of doses.
* sample population might not be independent/random.